---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../analysis.R")
```

## Introduction
Throughout the pandemic, many of us experienced pain and familiarized ourselves to new type of lifestyle due to **COVID-19**. We have finally produced vaccinations, yet there are growing concerns to these vaccines. Thorough this project, we aim to: 

1. Look through the data of _Covid-19 Vaccinations_ and _COVID-19 Deaths_ to see if there is any correlation between them.

2. We wish to find out about the _effectiveness of the COVID-19 vaccination_, and how it is differentiated throughout the _world_.

3. We aim to visualize through _effective graphs_, for us and our users to easily compare.

### Plot of Top 10 Countries with Highest Average Deaths
This plot shows the top 10 countries that had highest average deaths due to **COVID-19**. The data of countries have been visualized through bar graphs, with different colors to easily differentiate. In this graph, we are able to find out that **United States** had the highest average deaths, by nearly **_600,000_** deaths. Moreover, it is intriguing to find out that most of the countries that had highest deaths came from either _American continent_, or in the continent of _Europe_.

```{r, echo = F, message = F, include = T}
plot(plot_avg_deaths)
```

### Plot 2 of Distribution Variables

This plot shows the average number of vaccinations per month in the world. We can see that there is a positive trend, where the average number of vaccinations is increasing over time. In December 2020, the average number of vaccinations was **_165381.6_**, but it has increased to **_19646193.2_** vaccinations in May 2021. However, something that should be considered is that this trend may not be reflected when looking at different countries individually around the world. While this plot shows the overall average vaccination numbers for the world, different countries may show different numbers regarding the average number of vaccinations.

```{r, echo = F, message = F, include = T}
plot(avg_vaccinations_month_plot)
```


### Plot 1 of Relationships between Variables

This plot shows the _top 10 countries_ that had most new deaths in **May 2021** due to **COVID-19** and compares it to the total number of vaccinations for each respective country. The relationship between the two variables is visualized through a scatter plot, where each point represents a country. In this plot, we can see that **India** had the most new deaths, by nearly **_2,500_** deaths even though they have had the second highest number of vaccinations. Additionally, it is also interesting to see that _4_ of the _10_ countries with the most new deaths are in _South America_. Just looking at this graph there doesn't seem to be an immediate correlation between the total number and vaccinations and new deaths, however this could be due to the fact that these countries have vastly different population sizes and population densities. Going forward a correlation may be easier to see if the same visualization was created, but with countries of similar populations sizes and densities.

```{r deaths_vs_vaccinations_plot, echo=FALSE, fig.height=8, fig.width=8, paged.print=FALSE}
plot(deaths_vs_vaccinations_plot)
```

### Plot 2 of Relationships between Variables

```{r, echo = F, message = F, include = T}
plot(deaths_vs_months)
```
