---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
```

## Introduction
Throughout the pandemic, many of us experienced pain and familiarized ourselves to new type of lifestyle due to **COVID-19**. We have finally produced vaccinations, yet there are growing concerns to these vaccines. Thorough this project, we aim to: 

1. Look through the data of _Covid-19 Vaccinations_ and _COVID-19 Deaths_ to see if there is any correlation between them.

2. We wish to find out about the _effectiveness of the COVID-19 vaccination_, and how it is differentiated throughout the _world_.

3. We aim to visualize through _effective graphs_, for us and our users to easily compare.

### Plot of Top 10 Countries with Highest Average Deaths
This plot shows the top 10 countries that had highest average deaths due to **COVID-19**. The data of countries have been visualized through bar graphs, with different colors to easily differentiate. In this graph, we are able to find out that **United States** had the highest average deaths, by nearly **_600,000_** deaths. Moreover, it is intriguing to find out that most of the countries that had highest deaths came from either _American continent_, or in the continent of _Europe_.

```{r, echo = F, message = F, include = T}
plot(plot_avg_deaths)
```

### Plot 2 of Distribution Variables

```{r, echo = F, message = F, include = T}
plot(avg_vaccinations_month_plot)
```


### Plot 1 of Relationships between Variables

```{r deaths_vs_vaccinations_plot, echo=FALSE, fig.height=8, fig.width=8, paged.print=FALSE}
plot(deaths_vs_vaccinations_plot)
```

### Plot 2 of Relationships between Variables

```{r, echo = F, message = F, include = T}
plot(deaths_vs_months)
```
